### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@79107a123952c237f3db96b90f83940c59aee596 🚀

Software is structured based on DG.jl (\textbf{cite?}) and Dispersal.jl
(\textbf{cite?}).

Uses methods from EN.jl to generate metawebs, or can use empirical
networks from Mangal.jl (\textbf{cite?}).

Framework based on (\textbf{Velland2010ConSyn?}), processes divided into
four categories: selection, dispersal, drift, speciation.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
The Architecture of Biodiversity. \emph{Annual Review of Ecology,
Evolution, and Systematics}, 38, 567--593.

@@

@@

>>>>

\texttt{MetacommunityDynamics.jl} is built on \texttt{DynamicGrids.jl},
a library for high-performance gridded simulations in the \texttt{Julia}
language, and Dispersal.jl (Maino \emph{et al.} 2021), and extension of
\texttt{DynamicGrids.jl} specifically for modeling organism dispersal.
It also contains integrations with \texttt{EcologicalNetworks.jl}
(Poisot \emph{et al.} 2019) to generate metawebs, or can use empirical
networks from Mangal.jl (Banville \emph{et al.} 2021).

It implements the general framework for community dynamics proposed by
(\textbf{Velland2010ConSyn?}), where all community processes can divided
into four categories: selection, dispersal, drift, and speciation.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Banville2021ManJl}{}%
Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
EcologicalNetworks.jl: Two complementary packages for analyzing
ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
2721.

\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
The Architecture of Biodiversity. \emph{Annual Review of Ecology,
Evolution, and Systematics}, 38, 567--593.

@@

\leavevmode\hypertarget{ref-Maino2021PreGlo}{}%
Maino, J.L., Schouten, R. \& Umina, P. (2021). Predicting the global
invasion of Drosophila suzukii to improve Australian biosecurity
preparedness. \emph{Journal of Applied Ecology}, 58, 789--800.

@@

\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
Poisot, T., Bélisle, Z., Hoebeke, L., Stock, M. \& Szefer, P. (2019).
EcologicalNetworks.jl: Analysing ecological networks of species
interactions. \emph{Ecography}, 42, 1850--1861.
